Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-04-19 paper/tex/sections/methods.tex
methods updates

We use a population of binaries synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}. COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}. Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using the single star evolution fitting formulae from \citet{Hurley+2000} to the models of \citet{Pols+1998}. In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample. This algorithm increases the prevalence of target DCOs (BHBH, BHNS and NSNS binaries in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.

\subsubsection{Population overview}

The population of double compact objects used in this study was synthesised by \citet{Broekgaarden+2021}. One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.

@@

Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation. The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$. The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g. with][]{Sana+2012}. We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star. We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}. We assume that all binaries are circular at birth to reduce the dimensions of initial parameters. Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.

For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation and gravitational-wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL. We sample from these sets of parameters when creating synthetic galaxies.

@@

We assume that stars that undergo case BB mass transfer experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).

Stars with helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.

We assume that kicks are isotropic in the frame of the collapsing star. The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017}.
We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

\subsubsection{Physical assumptions in other models} \label{sec:variation_assumptions}
In addition to our fiducial model, we explore 14 other models which change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions. Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.

Models \modRangeMT{} focus on changes to the mass transfer physics. We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively. In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.

@@

\begin{table}[htb]
    \centering
    \begin{tabular}{cl}
        \hline \hline
        Model & Physics Variation \\
        \hline \hline
        \modFid & -- \\
        \hline
        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
        \modCaseBB & Case BB mass transfer is always unstable \\
        \hline
        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
        \modOpt & HG donor stars initiating a CE survive CE \\
        \hline
        \modRapid & Fryer rapid SN remnant mass prescription \\
        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
        \modNoPISN & PISN and pulsational-PISN not implemented \\
        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
        \modNoBH & Black holes receive no natal kick \\
        \hline \hline
    \end{tabular}%
    \caption{Adapted from \citet[][Table 2]{Broekgaarden+2021}, a description of the 15 binary population synthesis models used in this study. \modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics.}
    \label{tab:physics_variations}
\end{table}

@@

In order to produce a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries. For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc. We do not find that adding other components would significantly alter our results.

@@

\subsubsection{Milky Way disc model}

For the Milky Way thin disc, we use the model from \citet{Frankel+2018}. The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way. They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}. The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy. We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.

The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
\begin{equation}\label{eq:galaxy_tau}
    p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
\end{equation}
where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}. The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq. 5]{Frankel+2018}
\begin{equation}\label{eq:galaxy_R}
    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \cdot \frac{R_0}{[R_{\rm exp}(\tau)]^2},
\end{equation}
where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
\begin{equation}
    R_{\rm exp}(\tau) = 4 \unit{kpc} \qty(1 - \alpha_{R_{\rm exp}} \qty(\frac{\tau}{8 \unit{Gyr}})),
\end{equation}
where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
\begin{equation}\label{eq:galaxy_FeH}
    \begin{split}
        [{\rm Fe} / {\rm H}] (R, \tau) = &F_m + \nabla [{\rm Fe} / {\rm H}] R \\
        &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
    \end{split}
\end{equation}
where
\begin{equation}
    f(\tau) = \qty(1 - \frac{\tau}{\tau_m})^{\gamma_{[{\rm Fe} / {\rm H}]}},
\end{equation}
$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}. We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
\begin{equation}\label{eq:galaxy_FeH_to_Z}
    \log Z = 0.977 [{\rm Fe} / {\rm H}] + \log(Z_\odot).
\end{equation}
Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
\begin{equation}\label{eq:galaxy_z}
    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
\end{equation}
where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$. Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.

@@

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

@@

Each binary is likely to move from its birth orbit. Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw+1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.

>>>>

We use a population of binaries recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al. (in prep). This population is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep[][Team COMPAS: J. Riley et al. (in prep)]{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}. COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}. Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using fitting formulae from \citet{Hurley+2000} to the single star models of \citet{Pols+1998}.

@@

One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.

Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation. The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), $p(m_1) \propto m_1^{-2.3}$. The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g. with][]{Sana+2012}. We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star. We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}. We assume that all binaries are circular at birth to reduce the dimensions of initial parameters. Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}. In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample. This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.

For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL. We sample from these sets of parameters when creating synthetic galaxies.

@@

We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).

Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.

We assume that kicks are isotropic in the frame of the collapsing star. We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

\subsubsection{Model variations} \label{sec:variation_assumptions}
In addition to our fiducial model for the formation of DCOs, we explore 14 other models in which we change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions. Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.

Our fiducial model is labelled model \modFid{}. Models \modRangeMT{} focus on changes to the mass transfer physics. We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively. In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.

@@

\begin{table}[htb]
    \centering
    \begin{tabular}{cl}
        \hline \hline
        Model & Physics Variation \\
        \hline \hline
        \modFid & Fiducial (see Section~\ref{sec:fiducial_physics}) \\
        \hline
        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
        \modCaseBB & Case BB mass transfer is always unstable \\
        \hline
        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
        \modOpt & HG donor stars initiating a CE survive CE \\
        \hline
        \modRapid & Fryer rapid SN remnant mass prescription \\
        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
        \modNoPISN & PISN and pulsational-PISN not implemented \\
        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
        \modNoBH & Black holes receive no natal kick \\
        \hline \hline
    \end{tabular}%
    \caption{A description of the 15 binary population synthesis models used in this study. \modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics \citep[c.f.][Table 2]{Broekgaarden+2021}.}
    \label{tab:physics_variations}
\end{table}

@@

In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries described in Section~\ref{sec:COMPAS_explained}. For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc. We do not find that adding other components would significantly alter our results.

@@

\subsubsection{Milky Way disc model}\label{sec:disc_model}

For the Milky Way thin disc, we use the model from \citet{Frankel+2018}. The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way. They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}. The result of this work is a model for the Milky Way that is calibrated to observations and which includes the star formation history, radial birth profile and chemical enrichment history of the galaxy. We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.

The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
\begin{equation}\label{eq:galaxy_tau}
    p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
\end{equation}
where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}. The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq. 5]{Frankel+2018}
\begin{equation}\label{eq:galaxy_R}
    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \frac{R_0}{[R_{\rm exp}(\tau)]^2},
\end{equation}
where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
\begin{equation}
    R_{\rm exp}(\tau) = 4 \unit{kpc} \qty(1 - \alpha_{R_{\rm exp}} \qty(\frac{\tau}{8 \unit{Gyr}})),
\end{equation}
where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
\begin{equation}\label{eq:galaxy_FeH}
    \begin{split}
        [{\rm Fe} / {\rm H}] (R, \tau) &= F_m + \nabla [{\rm Fe} / {\rm H}] R \\
        &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
    \end{split}
\end{equation}
where
\begin{equation}
    f(\tau) = \qty(1 - \frac{\tau}{\tau_m})^{\gamma_{[{\rm Fe} / {\rm H}]}},
\end{equation}
$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}. We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
\begin{equation}\label{eq:galaxy_FeH_to_Z}
    \log_{10} (Z) = 0.977 [{\rm Fe} / {\rm H}] + \log_{10}(Z_\odot).
\end{equation}
Additionally, since this model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
\begin{equation}\label{eq:galaxy_z}
    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
\end{equation}
where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$. Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.

@@

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:disc_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

@@

Each binary is likely to move from its birth orbit. Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep{Hobbs+2005}.
